---
title: "PML Final Project"
author: "Shobeir K. S. Mazinani"
date: "February 14, 2016"
output: html_document
---

#Introduction:

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).


#Getting Data and loading packages:

```{r}
library(caret)
library(ggplot2)
```

We first download the datasets.
```{r}
url_train <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
url_test  <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
download.file(url_train, "pml-train.csv")
download.file(url_test, "pml-test.csv")
train_set <- read.csv("pml-train.csv")
test_set <- read.csv("pml-test.csv")
```

 Cross Validation


The next step is to devide the `train_set` into training and testing data sets. The `train_set` has `r dim(train_set)[1]` observations. We use a $70%$ of these to train our model and the rest for testing our model. Cross validation is achieved by splitting the training data into a test set and a training set using the following:
```{r}
inTrain <- createDataPartition(y=train_set$classe,p=0.7, list=FALSE)
training <- train_set[inTrain,]
testing <- train_set[-inTrain,]
```

# Predictions

We are trying the Random Forrest algorithem as implemented in the `caret` package to predict on our data sets.

```{r}
fit <- train (classe ~ .,training, preProcess = c("nzv"), na.action  = na.omit,method ="rf" )
testing <- na.omit(testing)
pred <- predict(fit,newdata = testing)
confusionMatrix(testing$classe,predict(fit,newdata = testing))
```

We can see from the testing that we are getting a nearly perfect model.
The Kappa value of $1$ is achieved. The importance of variables is as following.
```{r}
plot(varImp(fit, scale = FALSE))
```

